Detailed model description

### 2021-11-30 doc/appendix-model.Rmd
Start model appendix

### Matern parameterization

<!-- EW: Because of space limits, I might suggest moving all this to the SI -->
  The Matérn defines the covariance $\Phi \left( s_j, s_k \right)$ between spatial locations $s_j$ and $s_k$ as $\Phi\left( s_j,s_k \right) = \tau^2/\Gamma(\nu)2^{\nu - 1}
  (\kappa d_{jk})^\nu K_\nu \left( \kappa d_{jk} \right)$,
  <!-- TODO: paraphrase this to avoid self plagiarizing the synopsis report! -->
    where $\tau^2$ represents the spatial variance, $\Gamma$ represents the Gamma function, $K_\nu$ represents the Bessel function, $d_{jk}$ represents the Euclidean distance between locations $s_j$ and $s_k$, and $\kappa$ represents
  a scaling parameter that is estimated (REF).
  The parameter $\nu$ controls the smoothness of the covariance function.
  We set $\nu = 1$, which lets us take advantage of the Stochastic Partial Differential Equation (SPDE) approximation to the GMRF to greatly increase computational efficiency [@lindgren2011].

>>>>

\newcommand{\s}{\boldsymbol{s}}

## Notation conventions

This appendix uses the following notation conventions:

* Bold lowercase for vectors

* Bold subscript $\s$ since x, y

* Bold uppercase for matrices

* $\phi$ for all 'dispersion' parameters for consistency with code

* Family titles link to TMB or sdmTMB source code

* Attempt to link math symbols to argument options in model and code symbols

```{r, results='asis'}
symbols <- tibble::tribble(
  ~Symbol, ~Description,
  "$\\phi$",   "A dispersion parameter for a distribution",
  "$\\mu$",   "Mean",
  "$f$",   "Link function"
)
knitr::kable(symbols, caption = "Symbol notation and descriptions", escape = FALSE, format = "latex",  booktabs = TRUE)
```

```{r}
subscripts <- tibble::tribble(
  ~Symbol, ~Description,
  "$\\s$",   "Index for space; a vector of x and y coordinates",
  "$t$",   "Index for time",
  "$g$",   "Group"
)
knitr::kable(subscripts, caption = "Subscript notation", escape = FALSE, format = "latex",  booktabs = TRUE)
```
